\resumeSubheading
  {House of X}{Remote}
  {Software Development Engineer Intern}{Sep 2024 -- Dec 2024}{| \textit{React.js, Next.js, React Native, Strapi, Python, AWS}}
  \resumeItemListStart
    \resumeItem{Wearable Technology}
    {Worked with \textbf{Bluetooth Low Energy (BLE) protocols} to integrate a health monitoring wearable device with mobile application. Also wrote \textbf{Python} scripts for testing communication with the device.}
    \resumeItem{Mobile App Development}
    {Contributed to the development of \textbf{Genius}, a React Native fitness tracker app, focusing on integrating the wearable device and  crafting advanced animations to enhance user engagement and interactivity.}
    \resumeItem{E-commerce Frontend Development}
    {Developed and enhanced the \textbf{React.js} and \textbf{Next.js} based e-commerce frontend for influencer-led brands like \textbf{Blanko} (perfumes by King) and \textbf{YFLH} (kitchenware by Sanjyot Kheer). Implemented various user-focused features, ensuring seamless UI/UX.}
     \resumeItem{Product Launch Collaboration}
    {Collaborated with the \textbf{marketing team} for \textbf{two product launches}, creating detailed product pages with options for users to view \textbf{different product variants}, driving engagement and clarity for potential buyers.}

    \resumeItem{Automation and Optimization}
    {Developed \textbf{Node.js scripts} to streamline image optimization by converting assets to \textbf{WebP format} and automating their upload to \textbf{AWS S3}, improving load times and reducing manual tasks.}
    \resumeItem{Feature Development}
    {Collaborated across teams to deliver high-quality code, with \textbf{41 feature pull requests merged}, enhancing key functionalities and driving user interaction.}
  \resumeItemListEnd
