\resumeSubheading
  {Nomura | Global Markets Division – Fixed Income Structuring, End-User Computing Team}{Remote}
  {Intern}{[Month, Year] -- Present}{| \textit{FastAPI, Python, React.js, RxJS, Redux, VBA, IIS, Pydantic, Microservices, API Gateway, Git, Autosys, AG Grid, FlexLayout, Regex, JSON Pickle, OpenAPI}}
  \resumeItemListStart
    \resumeItem{Excel VBA Automation}
    {Developed automation scripts in \textbf{Excel VBA} to generate and send structured reports via Outlook, improving reporting efficiency.}
    \resumeItem{Codebase Modernization}
    {Migrated legacy \textbf{Python 3.6} codebase to \textbf{Python 3.11}, ensuring compatibility and performance enhancements.}
    \resumeItem{State Management Optimization}
    {Designed and implemented a \textbf{Redux-style state management system} using \textbf{RxJS and Observables}, improving application responsiveness.}
    \resumeItem{FastAPI Data Validation Enhancement}
    {Led the migration from \textbf{Pydantic v1 to v2}, optimizing data validation and serialization in FastAPI-based services.}
    \resumeItem{Dynamic Forms in React}
    {Developed \textbf{React-based dynamic forms} powered by JSON schema, enabling flexible UI configurations without hardcoded components.}
    \resumeItem{Automated Testing Improvements}
    {Automated \textbf{regression testing} with parameterized test cases, increasing test coverage and reliability.}
    \resumeItem{Deployment and Server Configuration}
    {Deployed and configured internal applications on \textbf{Windows Server with IIS}, ensuring stable production environments.}
    \resumeItem{Debugging and Version Control}
    {Utilized \textbf{Git Bisect} to debug and restore critical code when a teammate was unavailable, minimizing downtime.}
    \resumeItem{Workflow Automation}
    {Engineered a \textbf{DAG-based workflow automation system} in Python to streamline internal financial operations.}
    \resumeItem{High-Performance Data Tables}
    {Integrated \textbf{AG Grid Enterprise} for high-performance, interactive financial data tables in React applications.}
    \resumeItem{Real-Time Data Handling}
    {Enabled real-time data fetching and updates using \textbf{AbortController and Suspense in React}, enhancing user experience.}
    \resumeItem{Email Automation}
    {Developed an automation tool to trigger actions based on new \textbf{email arrivals in Outlook}, improving operational workflow.}
    \resumeItem{Embedded Document Rendering}
    {Rendered \textbf{Excel spreadsheets and PDFs directly within a React web application}, supporting financial data visualization.}
    \resumeItem{Hiring and Documentation}
    {Collaborated with cross-functional teams to screen and interview internship candidates, refining hiring processes. Documented deployment steps and best practices to improve onboarding and knowledge transfer for new team members.}
  \resumeItemListEnd
